Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalogue Data

### 2013-02-27 doc/references.tex
finalized draft
draft update

@@

@@

\bibitem[Krause et al.(2012)]{voids2} Krause, E., Chang, 
T.-C., Dor{\'e}, O., \& Umetsu, K.\ 2012, arXiv:1210.2446

@@

@@

@@

@@

@@

@@

>>>>

\bibitem[Auger(2008)]{Auger2008} Auger, M.~W.\ 2008, \mnras, 383, 
L40

@@

\bibitem[Fassnacht et al.(2006)]{FassnachtEtal2006} Fassnacht, C.~D., 
Gal, R.~R., Lubin, L.~M., et al.\ 2006, \apj, 642, 30

@@

@@

\bibitem[Kauffmann et al.(1999)]{KauffmannEtal1999} Kauffmann, G., 
Colberg, J.~M., Diaferio, A., \& White, S.~D.~M.\ 1999, \mnras, 303, 188
\bibitem[Krause et al.(2012)]{voids2} Krause, E., Chang, 
T.-C., Dor{\'e}, O., \& Umetsu, K.\ 2012, arXiv:1210.2446

@@

\bibitem[Koopmans et al.(2003)]{KoopmansEtal2003} Koopmans, L.~V.~E., 
Treu, T., Fassnacht, C.~D., Blandford, R.~D., 
\& Surpi, G.\ 2003, \apj, 599, 70

@@

\bibitem[Lagattuta et al.(2010)]{LagattutaEtal2010} Lagattuta, D.~J., 
Fassnacht, C.~D., Auger, M.~W., et al.\ 2010, \apj, 716, 1579

@@

\bibitem[Mandelbaum et al.(2009)]{Mandelbaum} Mandelbaum, R., van 
de Ven, G., \& Keeton, C.~R.\ 2009, \mnras, 398, 635

@@

\bibitem[Takahashi et al.(2011)]{TakahashiEtal2011} Takahashi, R., Oguri, 
M., Sato, M., \& Hamana, T.\ 2011, \apj, 742, 15

\bibitem[Treu et al.(2009)]{TreuEtal2009} Treu, T., Gavazzi, R., 
Gorecki, A., et al.\ 2009, \apj, 690, 670

@@

\bibitem[Wambsganss et al.(2004)]{WambsganssEtal2004} Wambsganss, J., 
Bode, P., \& Ostriker, J.~P.\ 2004, \apjl, 606, L93
